---
title: "Literature review classification"
output: 
  # beamer_presentation: default # https://bookdown.org/yihui/rmarkdown/beamer-presentation.html
   powerpoint_presentation: default # https://bookdown.org/yihui/rmarkdown/powerpoint-presentation.html
  # html_document: default
  # pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE, tidy = TRUE) # Parameters for chunks
# Loading Quanteda and readText to analyze unstructured text
library(quanteda)
library(readtext)
library(xlsx)

# Loading Todyverse to work with tables
library(tidyverse)

# Plotly to show results
# Source: https://plot.ly/r/table/
library(plotly)

# Decision tree for the classification function
library(tree)

#Random forest algorithm
library(randomForest)

# Sample testing for decision tree
# Source: https://www.r-bloggers.com/how-to-implement-random-forests-in-r/
library(rpart)
library(caret)
library(e1071)

```

# Introduction

The purpose of this paper is to determine how to automatically classify literature review genres.

# Methodology

We use the five step process of knowledge-discovery in database.

* Data Selection  
* Data Pre-processing
* Data Formatting
* Data mining
* Interpretation

```{r corpus}

### Abstracts from an CSV file
articles_info <- readtext("overall.csv", 
                     text_field = "Abstract_text"
                     )

articles <- corpus(articles_info)

### PDFs

# PDFDocs <- readtext("corpus_PDF/*.pdf", 
#                      text_field = "texts", 
#                      docvarsfrom = "filenames", # Extract variables from the title of the text
#                     dvsep = "_"
#                     )
# 
# names(PDFDocs) <- c("document", "text", "type", "article_ID","authors") 
# #Create corpus dataframe from extracted texts
# # This is needed to deal with different languages
# evidences_PDF <- corpus(PDFDocs)


### Loading the data from txt files
# # Source: https://tutorials.quanteda.io/import-data/multiple-files/
# 
# reflDocs <- readtext("corpus/*.txt",
#                      text_field = "texts",
#                      docvarsfrom = "filenames", # Extract variables from the title of the text
#                     dvsep = "_"
#                     )
# 
# #Rename extracted variables
# # The first 2 variables should not be changed
# 
# names(reflDocs) <- c("document", "text", "Type", "Article_ID","Authors")
# 
# #Create corpus dataframe from extracted texts
# # This is needed to deal with different languages
# 
# evidences <- corpus(reflDocs)

```

# Step 01: Data Selection

We start by performing text mining on `r length(articles_info$Authors)` abstracts of articles identified by Templier and Paré (2018). Link: https://www.tandfonline.com/doi/abs/10.1080/0960085X.2017.1398880

A polarized wordcloud allows to graphically assess whether there are word associated to one specific genre in the literature.

```{r wordcloud generator, out.width = '75%'}
# create a function to create WordClouds
myWordCloud <- function (dfm, myGroup){
# This function remove stopwords and punctuations, stem the words, 
# store the results in a frequency matrix and create a wordcloud
corpus(dfm)%>% # 
  dfm(groups = myGroup, remove = stopwords("english"), remove_punct = TRUE, stem = TRUE)%>% # Frequency matrix
  textplot_wordcloud(comparison = TRUE, max_words = 75) # Wordcloud graph
}

# World cloud for the different TYPES of literature review
set.seed(1)

myWordCloud(articles_info, "Type")

```

# Step 02: Data Pre-processing 

We start by associating to each abstract a set of information, and by analysis the frequency of appeareance of each word in the text.

```{r}
# Get list of docs and words and Convert to dataframe
# https://rdrr.io/cran/quanteda/man/as.data.frame.dfm.html
classifTable <- articles %>%
  dfm(groups = "Reference", remove = stopwords("english"), remove_punct = TRUE, stem = TRUE)%>%
  convert(to ="data.frame")

colnames(classifTable)[1] <- "Reference"

head(classifTable[,1:3], 1)
```


# Step 03: Data transformation

To perform an automatic classification, we add the type of review as a dependent variable.

```{r classification_Table}

myClassificationTable <- function(evidences, myTypes){
# Get list of docs and words and Convert to dataframe
# https://rdrr.io/cran/quanteda/man/as.data.frame.dfm.html
classifTable <- evidences %>%
  dfm(groups = "Reference", remove = stopwords("english"), remove_punct = TRUE, stem = TRUE)%>%
  convert(to ="data.frame")

colnames(classifTable)[1] <- "Reference"


# Add type in the first column
classification <- data.frame(
  "Type" = myTypes$Type,
  classifTable[,-1] # Removing the title and the id of documents
)

classification
}

# Get initial types of docs and Make a column with types of docs in the right order
myTypes <- data.frame(
                  "Reference"= articles$documents$Reference, 
                  "Type"= articles$documents$Type
                  )%>%
                  left_join(classifTable, by = "Reference")

classification <- myClassificationTable(articles, myTypes)

head(classification[,1:6])
```

# Step 04: Data mining

We use the decision tree algorithm to automatically extracts classification rules.
Other classification algorithms have been shown to be more effective for natural language processing, but here we are interested in the ability to extract a set of rules, which can be easily understood by humans.

```{r decision_tree_image, out.width = '75%'}
# decision tree (removing the "document" column to extract rules)
Classification_rules <- tree(Type ~.-Type, classification[,-2]) 

# Showing decision tree
plot(Classification_rules) 
text(Classification_rules)

Classification_rules
```

```{r misclassification}
misclassification <- as.numeric(format(round(          summary(Classification_rules)[7]$misclass[1]/summary(Classification_rules)[7]$misclass[2]          , 2), nsmall = 2))

summary(Classification_rules)
```
The misclassification rate is `r misclassification * 100`%.

## Predicting power of the decision tree algorithm
```{r}
# Source: https://www.datacamp.com/community/tutorials/decision-trees-R

set.seed(101)
train=sample(1:nrow(classification), nrow(classification)/2)

tree.abstracts = tree(Type~., classification[train,-2])
plot(tree.abstracts)
text(tree.abstracts, pretty=0)

tree.pred = predict(tree.abstracts, classification[-train,-2], type="class")

with(classification[-train,-2], table(tree.pred, Type))

summary(tree.pred)

```



```{r decision_tree_02, include=FALSE, eval=FALSE}

model_dt = train(Type ~., 
                data = classification[,-2], 
                method = "rpart"
                )

model_dt_1 = predict(model_dt, data = classification[,-2])

table(model_dt_1, classification$Type)

mean(model_dt_1 == classification$Type)

```

## Random Forest
As a complement, we run the random forest algorithm, which tests mutliple decision trees. 
```{r random_forest}

set.seed(1)

rf.model1 <- randomForest(Type ~., 
                       data = classification[train,-2], 
                       ntree = 500, 
                       mtry = 500,
                       importance = TRUE
                       )
rf.model1

rf.pred = predict(rf.model1, classification[-train,-2], type="class")

with(classification[-train,-2], table(tree.pred, Type))


```


```{r random_forest_graphs}

head(importance(model1))

varImpPlot(model1)
```


# Model 2: The classification done with 4 Types set by Rowe (2014) does not improve the results

```{r}
myWordCloud(articles_info, "Type_Rowe")


# Get initial types of docs and Make a column with types of docs in the right order
myTypes_Rowe <- data.frame(
                  "Reference"= articles$documents$Reference, 
                  "Type"= articles$documents$Type_Rowe
                  )%>%
                  left_join(classifTable, by = "Reference")

classification_Rowe <- myClassificationTable(articles, myTypes_Rowe)

# decision tree (removing the "document" column to extract rules)
Classification_rules_Rowe <- tree(Type ~.-Type, classification_Rowe[,-2]) 

# Showing decision tree
plot(Classification_rules_Rowe) 
text(Classification_rules_Rowe)

summary(Classification_rules)

model_Rowe <- randomForest(Type ~., 
                       data = classification_Rowe[,-2], 
                       ntree = 500, 
                       mtry = 500,
                       importance = TRUE
                       )
model_Rowe

```



# Step 05: interpretation

To be done


\newpage

# Appendix:

```{r result list, include=FALSE, eval=FALSE}
evidences <- articles

META <- corpus_subset(evidences, Type=="Meta")
CRITICAL <- corpus_subset(evidences, Type=="Critical")
DESCRIPTIVE <- corpus_subset(evidences, Type=="Descriptive")
QUALITATIVE <- corpus_subset(evidences, Type=="Qualitative")
THEORETICAL <- corpus_subset(evidences, Type=="Theoretical")
NARRATIVE <- corpus_subset(evidences, Type=="Narrative")
```

A more detailed analysis show differences between the words networks of
* Meta-Reviews
* Critical
* Descriptive
* Qualitative
* Theoretical
* Narrative

```{r textNetwork, out.width = '75%', include=FALSE, eval=FALSE}
## Detailed analysis of the overall Word network (min_freq=.95)

myWordNetwork <- function (dfm, myTermFreq, myMaxFreq, myMinFreq){
dfm %>%
  dfm(remove = stopwords("english"), stem = TRUE, remove_punct = TRUE) %>%
  dfm_select(min_nchar = 5) %>%
  dfm_trim(min_termfreq = myTermFreq, max_freq = myMaxFreq)%>%  
  fcm()%>%
  textplot_network(min_freq = myMinFreq)
}

# Parameters for word network visualization
myTermFreq <- 10 
myMaxFreq <- 0.7 
myMinFreq <- 0.9

# myWordNetwork(evidences, myTermFreq, myMaxFreq, myMinFreq)

# par(mfrow=c(3,2))

myWordNetwork(META, myTermFreq, myMaxFreq, myMinFreq)
myWordNetwork(CRITICAL, myTermFreq, myMaxFreq, myMinFreq)
myWordNetwork(DESCRIPTIVE, myTermFreq, myMaxFreq, myMinFreq)
myWordNetwork(QUALITATIVE, myTermFreq, myMaxFreq, myMinFreq)
myWordNetwork(THEORETICAL, myTermFreq, myMaxFreq, myMinFreq)
myWordNetwork(NARRATIVE, myTermFreq, myMaxFreq, myMinFreq)
```



